---
title: "Coding Scheme"
author: "andrés castro araújo"
date: "4/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reliability

```{r, message=FALSE}
library(tidyverse)
library(googlesheets4)
source("utilities.R")

url <- "https://docs.google.com/spreadsheets/d/1CUUyXMpQD2aTZdtgS7ah6nhIegPqRLEutIJgp0-vIYI/"
```

The `utilities.R` file has three functions:

-   `check_lenght()`

### Entity level

Read the data from Google Sheets

```{r}
andres <- read_sheet(ss = url, sheet = "andres") %>% 
  filter(!is.na(id)) %>% 
  mutate(coder = "andres") %>% 
  select(!entity_size)

aly <- read_sheet(ss = url, sheet = "aly") %>% 
  filter(!is.na(id)) %>% 
  mutate(coder = "aly") %>% 
  select(!entity_size)

lindsay <- read_sheet(ss = url, sheet = "lindsay") %>% 
  filter(!is.na(id)) %>% 
  mutate(coder = "lindsay") %>% 
  select(!entity_size)

```

**Check lengths:**

There should be 100% agreement on number of entities before proceeding to the other stuff.

```{r}
check_length(andres, aly, lindsay)
```

We can also do pairwise comparisons with the same function, which is what each of us will have to do for the double coding checking.

```{r}
check_length(andres, aly)
check_length(andres, lindsay)
check_length(aly, lindsay)
```

**Entity level variables:**

We can check the overall reliability with the `agreement()` function.

```{r}
df <- bind_rows(aly, andres, lindsay)

agreement(df, "type")
agreement(df, "race")
agreement(df, "marijuana_role")
agreement(df, "criminal_activity")
agreement(df, "cjs_involvement")
agreement(df, "decriminalization")
agreement(df, "med_involvement")
agreement(df, "legal_controversy")
```

We can now see the specific details using the `check_disagreements()` function

```{r}
check_disagreements(aly, lindsay, "legal_controversy")
check_disagreements(aly, lindsay, "race")
```

### Article level

Read the data from Google Sheets:

```{r}
andres_article <- read_sheet(ss = url, sheet = "andres_data") %>% 
  filter(!is.na(id), !remove) %>% 
  mutate(coder = "andres") 

aly_article <- read_sheet(ss = url, sheet = "aly_data") %>% 
  filter(!is.na(id), !remove) %>% 
  mutate(coder = "aly") 

lindsay_article <- read_sheet(ss = url, sheet = "lindsay_data") %>% 
  filter(!is.na(id), !remove) %>% 
  mutate(coder = "lindsay") 
```

See overall agreements

```{r}
df_article <- bind_rows(aly_article, andres_article, lindsay_article)

agreement(df_article, "date")
agreement(df_article, "entities")
agreement(df_article, "medicalization")
agreement(df_article, "cjs")
agreement(df_article, "calls_for")
agreement(df_article, "remove")
```

See more detail:

```{r}
check_disagreements(lindsay_article, andres_article, "calls_for")
```
